Mapping plant-pollinator interactions across Europe

### 2023-11-22 Manuscript/Ms.qmd
Updating pdf and scritps

# Ideas/objectives:

- Write article point by point

- Ecography could be our potential journal (think about it, high fees)

- Finish paper by Christmas

- Create workflow graph

>>>>

# Abstract

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time that allows to evaluate the consequences of environmental change on their conservation status and

conservation status of the different species and their responses to the different environmental changes. Although recent efforts have progressed towards this goal, Europe, one of the continents with higher number of plant-pollinator studies, still lacks

an open access and homogenised dataset of plant-pollinator interactions that serves as a baseline for future ecological research. Here, we provide

and explore the first European metaweb of plant-pollinator interactions. This is a continent-level metaweb that comprised of xxx plants xxx pollinators and xxxx interactions which covers xxxx different countries. We show that plant and pollinator species are xxxxx and have xxxxxxx. For instance, we cover xxx% of European bee species and xxx% of flowering plants that rely on pollinators.

# Introduction

1st paragraph

General introduction of how global change impacts plant-pollinator interactions

Maybe expand on some drivers? Climate change, habitat fragmentation, agricultural intensification, urbanization, pollution, pesticides and species' invasions

Highlight the relevance of large scale datasets

2nd paragraph

3rd paragraph

4paragraph

Introduce research questions

LIST THEM HERE (Main ideas so far)

Questions that we would like to answer:

1\) What are the most common plant a pollinator species? Are those shared across networks? Most common interactions across Europe? Interaction fidelity

2\) Is generalization the rule? Or specialization? How this impacts indirect interactions? Go in the direction of pollinator importance?

# Methods

# Results

# Discussion
